### 2012-10-23 rnaseq_paper.tex
added some numbers beside percentages in OasesM topic

The above approaches recovered transcript fragments, but not entire genes
(figure in suppl?)
To construct a more comprehensive gene set containing all of the
assembled contigs, we tried using Oases-M to merge the assemblies from
multiple $k$ values \cite{Schulz:2012je}.  While it has been
demonstrated that merged transcripts from multiple-k assemblies
contain more isoforms than those from any single $k$, the sensitivity
of Oases-M for recovering splice variants has not been fully
evaluated.
% @CTB what does this mean? ``not fully evaluated''?
We merged transcripts from our global assembly, above,
with Oases-M using a k-mer size of 27, and compared them with the
unmerged transcripts.  We then cross-validated using publicly
available ESTs, which were not used in our assembly.
The results show that
Oases-M and the unmerged assembly share about 95\% of the predicted
splice junctions, with 5\% disjoint.  Of these 5\%,
approximately 6\% of the Oases-M-specific splice junctions are
independently supported by ESTs, while 19\% of the unmerged splice
junctions are supported by ESTs.
% @CTB change from percent to total number, with percent in parantheses
This suggests that Oases-M probably
discards a number of real splice variants, although the unmerged
assembly is also missing some found by Oases-M.

>>>>

The above approaches recovered transcript fragments, but not entire genes
(figure in suppl?)
To construct a more comprehensive gene set containing all of the
assembled contigs, we tried using Oases-M to merge the assemblies from
multiple $k$ values \cite{Schulz:2012je}.  While it has been
demonstrated that merged transcripts from multiple-k assemblies
contain more isoforms than those from any single $k$, the sensitivity
of Oases-M for recovering splice variants has not been fully
evaluated.
% @CTB what does this mean? ``not fully evaluated''?
We merged transcripts from our global assembly, above,
with Oases-M using a k-mer size of 27, and compared them with the
unmerged transcripts.  We then cross-validated using publicly
available ESTs, which were not used in our assembly.
The results show that
Oases-M and the unmerged assembly share about 104,413 (95\%) of the predicted
splice junctions, with 5\% disjoint.  Of these 5\%,
approximately 421 (6\%) of the Oases-M-specific splice junctions are
independently supported by ESTs, while 1,607 (19\%) of the unmerged splice
junctions are supported by ESTs.
% @CTB change from percent to total number, with percent in parantheses
This suggests that Oases-M probably
discards a number of real splice variants, although the unmerged
assembly is also missing some found by Oases-M.
